% Authors who equally contributed to a publication are marked with a \textdagger.

\newcounter{publicationCounter}			% We set an publication counter, we can continue counting the publications when switchen from conferences to workshop etc.
\datedsubsection{}
{%
}
{%
	Journal Publications
}
{%
	\begin{enumerate}
		\item \textbf{Nikolai K\"ohler}$^{\dagger}$, Tim Daniel Rose$^{\dagger}$, Lisa Falk and Josch Konstantin Pauling. Investigating Global Lipidome Alterations with the Lipid Network Explorer. \emph{Metabolites}, 2021; 11(8), 488.
		%
		\item Haberl EM, Weiss TS, Peschel G, Weigand K, \textbf{K\"ohler N}, Pauling JK, Wenzel JJ, Höring M, Krautbauer S, Liebisch G, Buechler C. Liver Lipids of Patients with Hepatitis B and C and Associated Hepatocellular Carcinoma. \emph{International Journal of Molecular Sciences}. 2021; 22(10):5297
		%
		\item Sebastian Schramm, \textbf{Nikolai K\"ohler}, Wilfried Rozhon. Pyrrolizidine Alkaloids: Biosynthesis, Biological Activities and Occurrence in Crop Plants. \emph{Molecules}, 2019, 24, 498.
		%
		\setcounter{publicationCounter}{\value{enumi}}	% Remember the counts
	\end{enumerate}
}

\datedsubsection{}
{%
}
{%
	Preprints
}
{%
	\begin{enumerate}
		\item Sebastian Dieckmann, Akim Strohmeyer, Monja Willershäuser, Stefanie Maurer, Wolfgang Wurst, Susan Marschall, Martin Hrabe de Angelis, Ralf Kühn, Anna Worthmann, Marceline M Fuh, Joerg Heeren, \textbf{Nikolai Köhler}, Josch K. Pauling, Martin Klingenspor. Susceptibility to diet induced obesity at thermoneutral conditions is independent of UCP1. bioRxiv, 2021; doi: https://doi.org/10.1101/2021.06.30.450595
		\setcounter{publicationCounter}{\value{enumi}}	% Remember the counts
	\end{enumerate}
}
\bigskip
{\footnotesize $^{\dagger}$ These authors contributed equally to this work.}

